
%% jasonbhill-resume-2014-02.tex
%% jason@jasonbhill.com

\documentclass[letterpaper,10pt]{article}
\usepackage{amsmath,color}

\definecolor{darkblue}{rgb}{0,0,0.35}
\definecolor{lightgray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.4,0.4,0.7}

\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}

%% set spacings
%%\linespread{1.0} %% comment out this line if not using charter font
\usepackage[hmargin=2cm,vmargin=1.5cm]{geometry}
\newcommand{\vsp}{\vspace{2pc}}
\setlength\parindent{0pt} %% Sets indent space to 0
\renewcommand{\indent}{\hspace{3pc}}

\newcommand{\mblue}{\color{darkblue}}

\begin{document}

\pagestyle{empty}

{\large\mblue R\'esum\'e}\hfill{\Huge\mblue Jason B. Hill}
\break{\footnotesize jason@jasonbhill.com | www.jasonbhill.com | github.com/hilljb | 802-233-6490}


\section*{\mblue Technical Skills}

\vspace{-2.15pc} {\hfill\mblue\rule{5.37in}{0.02cm}}

\vspace{1pc}\textbf{Languages/Libs/APIs:} Python, Cython, C/C++, OpenMP, MPI, Boost, udev/sysfs,
SCSI Generic (SG), pandas, BASH, R

\bigbreak\textbf{OS:} Enterprise: SLES, RHEL, CentOS\qquad Personal: OpenSUSE, Debian, Ubuntu\qquad
Devel: VirtualBox, Kiwi, OBS, APT

\bigbreak\textbf{High Performance Technical Computing (HPTC):}\quad Experience coding for up to
405,504-core distributed CPU/GPGPU systems, 4,096-core shared-memory single-image Linux systems,
fixed-topology supercomputers, multi-controller HA RAID/MAID/JBOD SCSI-target devices, Amazon EC2,
and commodity workstations.

\section*{\mblue Work Experience}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.245in}{0.02cm}}

\vspace{1pc}
\textbf{SGI (Silicon Graphics International)}\quad June 2013--present\hfill Longmont, CO

\bigbreak
\textit{Modular Infinite Storage -- Data Path Team}

\begin{itemize}
\item Led development and testing of SCSI Enclosure Services (SES) module (C/Cython backend with
Python module frontend). Integrated the module with C++/BoostPython for environmental monitoring and
enclosure services control on the Modular Infinite Storage scale-out storage/compute platform.

\item Wrote Massive Array Idle Disk (MAID) drive power [C] library for the Kokopelli project.

\item In charge of data path related system event logging for notification and system management.
Wrote syslog event service [C++/Boost] and led event definition and cataloging management.

\item Various: researched random IO cache algorithms for SSD/NVDIMM cache, automated target iSCSI
port and Infiniband setup in OpenSUSE/SLES, tested Linux-HA solutions (e.g., Datera/RTSos, SLES HA,
Pacemaker/Corosync).
\end{itemize}

\vspace{1pc}
\textbf{University of Colorado Boulder}\quad 2006--2013\hfill Boulder, CO

\bigbreak
\textit{Graduate Student / Doctoral Candidate / Instructor of Mathematics}

\begin{itemize}
\item Computational/algorithms research talks: 2 talks at international conferences, 2 invited talks
at research institutions, 1 talk at Rocky Mountain Section Meeting of Mathematical Association of
America, 29 seminar presentations at CU-Boulder and nearby universities, 7 hour-long guest lectures
in CSCI6454 (graduate advanced algorithms).

\item Instructor of record for 14 undergraduate courses (multivariable calculus,
integral calculus, differential calculus, precalculus, college algebra, mathematics for the
environment, finite mathematics, spirit and uses of mathematics).

\item Instructor of record for 2
graduate courses (math teacher training, math teacher training seminar).

\item Root administrator
of sage.colorado.edu, a Sage Notebook server for the University of Colorado community.
\end{itemize} 


\section*{\mblue Education}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.845in}{0.02cm}}

\vspace{1pc}
\textbf{Ph.D. Mathematics (ABD)} -- computational group \& graph theory\hfill University
of Colorado Boulder

Working under Keith Kearnes and Alexander Hulpke to develop and implement parallel partition
backtrack algorithms for graph isomorphism generalizations on large degree permutation
representations.

\bigbreak \textbf{M.A. Mathematics (2010)} -- computational group theory, representation
theory\hfill University of Colorado Boulder

\bigbreak \textbf{M.S. Mathematics (2006)} -- computational number theory\hfill University of
Vermont

Developed and implemented an algorithm to locate an instance of the smallest absolute value
discriminant totally real number field of prime degree satisfying a given property. Used this
algorithm to discover the first known totally real quintic number field having minimal signature
group rank.

\bigbreak \textbf{B.S. Mathematics (2004)}\hfill University of Michigan-Flint


\section*{\mblue Personal Projects}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.21in}{0.02cm}}

\vspace{1pc}
\begin{itemize}
\item Big Data

\begin{itemize}
\item TweetWatch (github.com/hilljb/tweetwatch) -- A Python module giving access to Twitter's
streaming API and providing analytics of received data. Licensed under the LGPL and developed in
partnership with Room 214, a digital marketing and social media agency in Boulder, Colorado.

\item Collected data and performed analyses of social media activity during several large-scale
events: 99.997\% of Twitter activity related to the 2014 Sochi Olympic Games, minute-by-minute
analyses of the Tour de France, 2014 Super Bowl, 2013 NCAA ``March Madness,'' etc.

\item Won an `Analyze Boulder' data analysis challenge by collecting geographically tagged
social media references to `beer' in 70 languages over the span of one week and providing
visualizations of the collected data.

\item Presented a new randomized (Las Vegas) partition backgrack graph search algorithm at the 5th de
Br\'un Workshop on Groups, Combinatorics, and Computing. NUI Galway, Ireland, 2011. 
\end{itemize}

\item Sage (www.sagemath.org) -- Permutation group code development, GAP integration, notebook
development and deployment (2010--present). Sage is a free open-source mathematics software system
licensed under the GPL.

\item PyTableaux (github.com/hilljb/pytablueax) -- A Python module for \LaTeX\ combinatorics
typesetting. 
\end{itemize}


\section*{\mblue Publications}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.64in}{0.02cm}}

\vspace{1pc}
\begin{itemize}
\item \'O Cath\'ain, Padraig, and Hill, Jason B., ``On the Classification of Hadamard Matrices of Order
$4p$'', In preparation.
\item Hill, Jason B., \textit{On Finding Totally Real Quintic Number Fields of Minimal Signature
Group Rank}, MS Thesis, University of Vermont, Burlington, 2006. Print.
\item Hill, Jason B., ``Salvaging \textit{La G\'eom\'etrie}'', \textit{Meteorite}, Volume 4 (2004)
17--32. Print.
\end{itemize}


\section*{\mblue Workshops}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.76in}{0.02cm}}

\vspace{1pc}
\begin{itemize}
\item OpenACC GPU Programming Workshop (October, 2012) -- Pittsburgh Supercomputing Center
\item Sage Education Days 3 (June, 2011) -- University of Washington
\item Sage Notebook Days 31 (June, 2011) -- University of Washington
\item Sage Combinat Days 20.5 (May, 2010) -- Fields Institute, Toronto, Canada
\end{itemize}

\end{document}
