
%% jasonbhill-resume-2014.tex
%% jason@jasonbhill.com

\documentclass[letterpaper,10pt]{article}
\usepackage{amsmath,color}

\definecolor{darkblue}{rgb}{0,0,0.35}
\definecolor{lightgray}{rgb}{0.5,0.5,0.5}
\definecolor{lightblue}{rgb}{0.4,0.4,0.7}

\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}

%% set spacings
%%\linespread{1.0} %% comment out this line if not using charter font
\usepackage[hmargin=2cm,vmargin=1.5cm]{geometry}
\newcommand{\vsp}{\vspace{2pc}}
\setlength\parindent{0pt} %% Sets indent space to 0
\renewcommand{\indent}{\hspace{3pc}}

\newcommand{\mblue}{\color{darkblue}}

\begin{document}

\pagestyle{empty}

{\large\mblue R\'esum\'e}\hfill{\Huge\mblue Jason B. Hill}
\break{\footnotesize jason@jasonbhill.com | www.jasonbhill.com | github.com/hilljb | 802-233-6490}


\section*{\mblue Technical Skills}

\vspace{-2.15pc} {\hfill\mblue\rule{5.37in}{0.02cm}}

\vspace{1pc}
\hspace{-0.5pc}\begin{tabular}{lrl}
\textbf{Languages/APIs:} & expert: & Python, C, Cython, \LaTeX, Sage\cr
 & working: & C++, OpenMP, MPI, Boost, SCSI Generic (SG), pandas, R\cr
 & & \cr
\textbf{OS:} & enterprise: & SLES and variants (e.g., OpenSUSE), RHEL and variants (e.g., CentOS)\cr
 & personal: & Debian GNU/Linux\cr
 & experience: & Mac OS X, Windows 3.1+, OpenSolaris/OpenIndiana
\end{tabular}

\bigbreak\textbf{High Performance Technical Computing (HPTC):}\quad Experience coding for up to
405,504-core distributed CPU/GPGPU systems, 4,096-core shared-memory single-image Linux systems,
fixed-topology supercomputers, multi-controller high availability SCSI-target devices, Amazon EC2,
and commodity workstations.


\section*{\mblue Education}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.845in}{0.02cm}}

\vspace{1pc}
\textbf{Ph.D. Mathematics (ABD/2014)} -- computational group \& graph theory\hfill University
of Colorado Boulder

\bigbreak \textbf{M.A. Mathematics (2010)} -- computational group theory, representation
theory\hfill University of Colorado Boulder

\bigbreak \textbf{M.S. Mathematics (2006)} -- computational algebraic number theory\hfill University of
Vermont

\bigbreak \textbf{B.S. Mathematics (2004)}\hfill University of Michigan-Flint


\section*{\mblue Work Experience}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.245in}{0.02cm}}

\vspace{1pc}
\textbf{SGI (Silicon Graphics International)}\quad June 2013--present\hfill Longmont, CO

\bigbreak
\textit{Modular Infinite Storage -- Kokopelli Project}

\begin{itemize}
\item Led development and testing of SCSI Enclosure Services (SES) Python module. \textit{Details:
Backend in Cython using Linux SCSI Generic C headers and sgutils library implementation. Integration
in C++ using Boost Python. Designed for environmental monitoring and enclosure services control of
any SES-3 device.}

\item Wrote Massive Array Idle Disk (MAID) drive power library. \textit{Details: Written in C. Controls
disk drive power at the enclosure service level.}

\item Led system event logging management for the data path team. \textit{Details: Backend in C++
with Boost. Shared library integration using Cython for simultaneous Python and C++ object oriented
functionality from a single codebase.}

\item Various: researched random IO cache algorithms for SSD/NVDIMM cache, automated target iSCSI
port and Infiniband setup in OpenSUSE/SLES, tested Linux-HA solutions (e.g., Datera/RTSos, SLES HA,
Pacemaker/Corosync).
\end{itemize}

\vspace{1pc}
\textbf{University of Colorado Boulder}\quad September 2006--present\hfill Boulder, CO

\bigbreak
\textit{Graduate Student / Doctoral Candidate / Instructor of Mathematics}

\begin{itemize}
\item Computational/algorithms research talks: 2 talks at international conferences, 2 invited talks
at research institutions, 1 talk at Rocky Mountain Section Meeting of Mathematical Association of
America, 29 seminar presentations at CU-Boulder and nearby universities, 7 hour-long guest lectures
in CSCI6454 (graduate advanced algorithms).

\item Instructor of record for 14 undergraduate courses (multivariable calculus,
integral calculus, differential calculus, precalculus, college algebra, mathematics for the
environment, finite mathematics, spirit and uses of mathematics).

\item Instructor of record for 2
graduate courses (math teacher training, math teacher training seminar).

\item Root administrator
of sage.colorado.edu, a Sage Notebook server for the University of Colorado community.
\end{itemize} 


\section*{\mblue Other Work}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.7in}{0.02cm}}

\vspace{1pc}
\begin{itemize}
\item Instructor -- Mathematics, Pre-Collegiate Development Program\hfill CU Boulder, Colorado\quad 2010
\item Contract Software Engineer -- The Optical Sciences Company\hfill Anaheim, California\quad 2009
\item Instructor -- Digital Photography, Science Discovery Summer Camp\hfill CU Boulder,
Colorado\quad 2007, 2008
\item Contract Software Engineer -- The Booth Company\hfill Boulder, Colorado\quad 2007
\item Adjunct Instructor -- Mathematics, Saint Michael's College\hfill Colchester, Vermont\quad 2006
\item Adjunct Instructor -- Photography, Community College of Vermont\hfill Newport, Vermont\quad 2006
\item Contract Photographer -- Automobile Magazine\hfill Ann Arbor, Michigan\quad 2004
\item Contract Software Engineer -- JP Engineering\hfill Traverse City, Michigan\quad 2002--2006
\end{itemize}


\section*{\mblue Personal Projects}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.2in}{0.02cm}}

\begin{itemize}
\item Big Data

\begin{itemize}
\item TweetWatch (github.com/hilljb/tweetwatch) -- A Python module giving access to Twitter's
streaming API and providing analytics of received data. Licensed under the LGPL and developed in
partnership with Room 214, a digital marketing and social media agency in Boulder, Colorado.

\item Collected data and performed analyses of social media activity during several large-scale
events: 99.997\% of Twitter activity related to the 2014 Sochi Olympic Games, minute-by-minute
analyses of the Tour de France, 2014 Super Bowl, 2013 NCAA ``March Madness,'' etc.

\item Won an `Analyze Boulder' data analysis challenge by collecting geographically tagged
social media references to `beer' in 70 languages over the span of one week and providing
visualizations of the collected data.

\item Presented a new randomized (Las Vegas) partition backgrack graph search algorithm at the 5th de
Br\'un Workshop on Groups, Combinatorics, and Computing. NUI Galway, Ireland, 2011. 
\end{itemize}

\item Sage (www.sagemath.org) -- Permutation group code development, GAP integration, notebook
development and deployment (2010--present). Sage is a free open-source mathematics software system
licensed under the GPL.

\item PyTableaux (github.com/hilljb/pytablueax) -- A Python module for \LaTeX\ combinatorics
typesetting. 
\end{itemize}


\section*{\mblue Publications}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.64in}{0.02cm}}

\vspace{1pc}
\begin{itemize}
\item \'O Cath\'ain, Padraig, and Hill, Jason B., ``On the Classification of Hadamard Matrices of Order
$4p$'', In preparation.
\item Hill, Jason B., \textit{On Finding Totally Real Quintic Number Fields of Minimal Signature
Group Rank}, MS Thesis, University of Vermont, Burlington, 2006. Print.
\item Hill, Jason B., ``Salvaging \textit{La G\'eom\'etrie}'', \textit{Meteorite}, Volume 4 (2004)
17--32. Print.
\end{itemize}


\section*{\mblue Workshops}

\vspace{-2.15pc}
{\hfill\mblue\rule{5.76in}{0.02cm}}

\vspace{1pc}
\begin{itemize}
\item OpenACC GPU Programming Workshop (October, 2012) -- Pittsburgh Supercomputing Center
\item Sage Education Days 3 (June, 2011) -- University of Washington
\item Sage Notebook Days 31 (June, 2011) -- University of Washington
\item Sage Combinat Days 20.5 (May, 2010) -- Fields Institute, Toronto, Canada
\end{itemize}

\end{document}
